Computer-Assisted Analysis of the \\ Anderson-Hájek Ontological Controversy

### 2017-01-06 Papers/2017/LogicaUniversalis-HajekAndersonControversy/main.tex
Improve conclusion

\section{Conclusion}
Using our approach, that is, semantical embeddings of variants of higher-order
modal logics in classical higher-order logic, the formalization and
(partly) automated analysis of several variants of G\"odel's
ontological argument has been surprisingly straightforward. The
higher-order provers we employed not only confirmed many claimed results, but also exposed a
few mistakes and novel insights in a long standing controversy.  We
believe the technology employed in this work is ready to be fruitfully
adopted in larger scale by philosophers.  Moreover, our approach is
by no means restricted to metaphysics or philosophy, and further work
includes similar applications in other areas, including, for example,
law, politics and ethics. In fact, we claim, that our approach, at
least to some degree, realizes Leibniz' dream of a characteristica universalis
and calculus ratiocinator.

>>>>

\section{Conclusion}
Using our approach of semantically embedding higher-order
modal logics in classical higher-order logic, the formalization and
(partly) automated analysis of several variants of G\"odel's
ontological argument has been surprisingly straightforward. The
higher-order provers we employed not only confirmed many claimed results, but also exposed a
few mistakes and novel insights in a long-standing controversy.  We
believe the technology employed in this work is ready to be fruitfully
adopted in larger scale by philosophers.  Moreover, our approach is
by no means restricted to metaphysics or philosophy, and further work
could explore similar applications in other areas, including, for example,
law, politics and ethics. In fact, we claim that our approach, at
least to some degree, realizes Leibniz's dream of a characteristica universalis
and a calculus ratiocinator.
